### 2020-01-13 fragments/wisdom_et_al_2016.tex
merged in fragments of arjovsky et al 2016

>>>>

(arjovsky_unitary_2016)
vanishing gradients adversely affect credit assignment function of backpropagation
explicitly derive the upper bound on the norm of the gradient wrt intermediate recurrent outputs
as a a function of depth (through extensive use of the chain-rule, and the definition of the
operator norm of a square matrix; and if intermediate output grads die/explode, then the grad wrt
the weight of the layers tends to die/explode). Thus they motivate the use of unitary (orthogonal)
weight matrices.

Note that in their experiments, split-re-im ReLU adversely affected the performance by
``brutally'' destroying the pahse, and so the decision was made to use modReLU, that applies
the rectifier to the amplitude of a complex number.

Finally, they use a mixing layer to transform complex to real outputs as in \cite{wolter_yao_2018}.
